Stack Safety is a Security Property

### 2021-04-14 tex/main.tex
Minor changes

The separation is less useful\bcp{but still sensible, right} in protection mechanisms that interact more directly
with application code, such as Cheri-style capabilities\citep{??}\bcp{This
  section would read better if we could cleanly separate the general
  definitions from examples}. Here
the policy would not have auxiliary state, but would still refine the machine step
function to create a distinct failstop condition. Other techniques such as
software fault isolation~\citep{??} might never actually failstop, but fulfill
the properties by rewriting code so that traces can never violate them.

>>>>

The separation is smaller in protection mechanisms that interact more directly
with application code. Some mechanisms might exhibit failstop behavior, but have
no protected policy state; others might never even failstop. Then the policy-enhanced
machine is simply identical to the original. This is the case for software-based
techniques.
